On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-04 main.tex
minor tweaks

% packages 
%\usepackage[options ]{algorithm2e}
\usepackage[ruled,vlined]{algorithm2e}
%\usepackage{algorithm,algpseudocode,float}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{enumitem}
% new commands and shortcuts
\def\td{{\bf todo}}
\def\bs{\textit{\textbf{s}}}
\def\bz{\textit{\textbf{0}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\Lambdab{\bm{\Lambda}}
\def\Thetab{\bm{\Theta}}
\def\thetab{\bm{\vartheta}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\pb{\textit{\textbf{p}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\pr{\mathbb{P}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textrm{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\kt{\widetilde{k}}
\def\dt{s}
%% \def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
\section{Introduction}
\subsection{Problem statement}
Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth. We provide bit-complexity estimates for computing one point in each connected component of $V(f)\cap \R^n.$ Its boolean complexity is $\hdots$.
\subsection{Motivation}
\subsubsection{Applications}
Computing one point in each connected component of the real part of a hypersurface is a basic and important subroutine used in semi-algebraic geometry. For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface, and it is used in determining whether or not a complex hypersurface has real solutions. 
\subsubsection{Bit-complexity}
Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work. As bit complexity provides a far more realistic model of computation compared to arithmetic complexity,  which only counts each operation at unit cost, our results therefore begin to fill an important missing gap in the research. 

@@

boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most

@@

\textbf{The boolean cost:} The following lists the costs for each step of Algorithm 1:

@@

    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the following upper bound on the total boolean cost of the algorithm:

>>>>

% packages 
%\usepackage[options ]{algorithm2e}
\usepackage[ruled,vlined]{algorithm2e}
%\usepackage{algorithm,algpseudocode,float}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{enumitem}
% new commands and shortcuts
\def\td{{\bf todo}}
\def\bs{\textit{\textbf{s}}}
\def\bz{\textit{\textbf{0}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\Lambdab{\bm{\Lambda}}
\def\Thetab{\bm{\Theta}}
\def\thetab{\bm{\vartheta}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\pb{\textit{\textbf{p}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\pr{\mathbb{P}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textrm{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\kt{\widetilde{k}}
\def\dt{s}
%% \def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\softO}{{O^{\sim}}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
%
%
%
%
\section{Introduction}
%
\subsection{Problem statement}
%
Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth. We provide bit-complexity estimates for computing one point in each connected component of $V(f)\cap \R^n.$ Its bit complexity is $\hdots$.
%
\subsection{Motivation}
%
\subsubsection{Applications}
%
Computing one point in each connected component of the real part of a hypersurface is a basic and important subroutine used in semi-algebraic geometry. For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface, and it is used in determining whether or not a complex hypersurface has real solutions.

\subsubsection{Bit-complexity}
Algorithms for deciding connectivity queries in real algebraic geometry
have been developed in a series of papers
\cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However,
these algorithms are based in the arithmetic complexity model, and bit
complexity questions have been left for future work. As bit complexity
provides a far more realistic model of computation compared to arithmetic
complexity,  which only counts each operation at unit cost and does not
account for coefficient size, our results therefore address an important
missing aspect of previous research.

Note that by the bit complexity we mean to count the number of all machine
operations require on a standard computer in terms of the length of a
standard representation (accounting for coefficient size, etc.).  In
particular, we assume that an integer $a\in\ZZ$ is represented with
$O(\log|a|)$ bits, and operations on integers with $\ell$ bits require
$\softO(\ell)$ bit operations.

@@

bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most

@@

\textbf{Bit operation cost:} The following lists the costs for each step of Algorithm 1:

@@

    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the
    following upper bound on the total number of bit operations required by the algorithm:
